Effects of resonant and random excitations on the proton beam in the Large Hadron Collider with applications to active halo control with pulsed hollow electron lenses

### 2018-09-15 response.tex

\usepackage{bm}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks=true, allcolors=NavyBlue]{hyperref}

\usepackage{mathptmx}
\linespread{1.1}            
\usepackage[T1]{fontenc}

\setlength{\parindent}{0ex}
\setlength{\parskip}{0.5\baselineskip}

\newcommand{\q}[2]{\ensuremath{#1\ \mathrm{#2}}} % quantity with units
\newcommand{\code}[1]{\textsc{#1}} % computer code
\newcommand{\note}[1]{\emph{\textcolor{red}{#1}}} % note, to-do

% environment for editorial or referee comments
\newenvironment{co}{\em}{}
\newcommand{\bco}{\begin{co}}
\newcommand{\eco}{\end{co}}

% environment for responses
\newenvironment{re}{\color{NavyBlue}}{}
\newcommand{\bre}{\begin{re}}
\newcommand{\ere}{\end{re}}

@@

Best regards,

Giulio Stancari\\
\emph{Corresponding author}\\
\texttt{stancari@fnal.gov}

\section*{Editorial comments}

\bco
We [\ldots] suggest that Reference [5] should be updated to a
journal article:

@@

[5b] M. Benedikt and F. Zimmermann, ``FCC: Colliders at the Energy
Frontier,'' Proc. IPAC2018, Vancouver.
\eco

\bre
The references were updated.
\ere

\section*{Problems with manuscript}

\bco In reviewing the figures of your paper, we note that the
  following changes would be needed in order for your figures to
  conform to the style of the Physical Review.  Please check all
  figures for the following problems and make appropriate changes in
  the text of the paper itself wherever needed for consistency.\eco

@@

\begin{description}

\bco
\item[Figure(s) 3, 13, 21, 25, 29] The abbreviation ``a.u.'' is used
  to indicate atomic units only; arbitrary units are abbreviated
  ``arb.  units''; ``A.U.'' is for astronomical units; ``amu'' is for
  atomic mass units.  Please amend your figures and manuscript text
  accordingly.
\eco

\note{(Miriam.)}

\bco
\item[Figure(s) 4] The size and font of the letters and numbers
  appearing in figures should be uniform (or close to it).  Please
  make the letters and numbers more consistent.
\eco

\bre Done.\ere

\bco
\item[Figure(s) 4, 11] Please change E1, E2, etc., to power of 10
  notation (i.e., 10 with appropriate superscript).  We do not print
  computer notation.
\eco

\bre Done for Fig.~4. \ere \note{Miriam, could you please take care of Fig.~11?}

\bco
\item[Figure(s) 9, 10, 16, 23, 26] Please modify quantities so that
  superscripts and subscripts are set as they would appear in
  text. Subscripts should be printed below the line. Also, we do not
  print computer notation. For example, set powers as superscript
  numbers; do not use \verb!^2!, \verb!**2!, etc., for squares of
  quantities. Please adjust the text of the paper accordingly.
\eco

\note{This comment is a bit extreme. Miriam, could you emphasize the
  difference between text and subscripts?}

\bco
\item[Figure(s) 9, 10, 16, 23, 26] The lettering in the axis labels
  and/or numbering size should be increased.
\eco

\note{Miriam.}

\bco
\item[Figure(s) 13, 21, 25, 29] Please rearrange power of 10 in axis
  label for clarity: Either (i)~place the power of 10 as a factor,
  without parentheses, in front of the axis label quantity, changing
  the sign of the power as needed; or (ii)~incorporate the power of 10
  in the topmost or rightmost number on the scale.  Please refer to
  the URL
  \url{http://journals.aps.org/authors/axis-labels-and-scales-on-graphs-h18}
  for a pictorial representation of the preferred forms for axis
  labels.
\eco

\note{Miriam.}

\bco
\item[Figure(s) 23, 26] Please insert post-decimal zeros (1.0, not 1.)
  or delete the decimal point.
\eco

\note{Miriam.}

\end{description}

\bco
TITLE:

This journal does print title footnotes.  Move informatio into your
acknowledgments section.
\eco

\bre Done.\ere

\bco
The following problems were noted in your manuscript.

\begin{itemize}
\item Please check the changes made to the title of your manuscript.
  We propose a modified and somewhat shorter title.
\end{itemize}
\eco

\bre We slightly shortened the title. However, the authors feel that
``active halo control'' is an important concept that should be
emphasized in the title. \ere

@@

\section*{Report of Referee A}

\bco
The paper describes quite extensive simulation and experimental work 
in estimating the effects of either resonant or random dipole 
excitations on the LHC proton beam at injection. Quantities studied 
include beam loss, transverse beam profiles, and bunch length. The 
studies are motivated by the planned use of a hollow electron lens in 
the HL-LHC in pulsed mode (either resonantly with the betatron tune, 
or randomly). The pulsed mode should deplete the beam halo but not 
affect the beam core.

### 2018-09-15 resex.tex
Modified title and acknowledgments. Updated response letter.

\title{Effects of resonant and random excitations on the proton beam
  in the Large Hadron Collider, with applications to the design of
  pulsed hollow electron lenses for active halo control}

\thanks{This manuscript has been authored by Fermi Research Alliance,
  LLC under Contract No.~DE-AC02-07CH11359 with the U.S.\ Department
  of Energy (DOE), Office of Science, Office of High Energy
  Physics. This work was partially supported by the U.S.\ DOE LHC
  Accelerator Research Program (LARP), by the European FP7 HiLumi LHC
  Design Study, Grant Agreement 284404, and by the High Luminosity LHC
  (HL-LHC) Project.}

@@

  This work was made possible by the High Luminosity LHC (HL-LHC)
  Project, the HiLumi LHC Design Study, and by the United States
  Department of Energy LHC Accelerator Research Program (LARP).
\end{acknowledgments}

>>>>

\title{Effects of resonant and random excitations on the proton beam
  in the Large Hadron Collider with applications to active halo
  control with pulsed hollow electron lenses}

@@

  This manuscript has been authored by Fermi Research Alliance,
  LLC under Contract No.~DE-AC02-07CH11359 with the U.S.\ Department
  of Energy (DOE), Office of Science, Office of High Energy
  Physics. This work was partially supported by the U.S.\ DOE LHC
  Accelerator Research Program (LARP), by the European FP7 HiLumi LHC
  Design Study, Grant Agreement 284404, and by the High Luminosity LHC
  (HL-LHC) Project.
\end{acknowledgments}
